Selección de Instancias

### 2015-05-04 doc/paper.tex
paper

\begin{abstract}
\end{abstract}

@@

\section{\label{sec:level1}First-level heading}

This sample document demonstrates proper use of REV\TeX~4.1 (and
\LaTeXe) in manuscripts prepared for submission to AIP
journals. Further information can be found in the documentation included in the distribution or available at
\url{http://authors.aip.org} and in the documentation for 
REV\TeX~4.1 itself.

When commands are referred to in this example file, they are always
shown with their required arguments, using normal \TeX{} format. In
this format, \verb+#1+, \verb+#2+, etc. stand for required
author-supplied arguments to commands. For example, in
\verb+\section{#1}+ the \verb+#1+ stands for the title text of the
author's section heading, and in \verb+\title{#1}+ the \verb+#1+
stands for the title text of the paper.

Line breaks in section headings at all levels can be introduced using
\textbackslash\textbackslash. A blank input line tells \TeX\ that the
paragraph has ended.

@@

\subsubsection{\label{sec:level3}Third-level heading: Citations and Footnotes}

Citations in text refer to entries in the Bibliography;
they use the commands \verb+\cite{#1}+ or \verb+\onlinecite{#1}+. 
Because REV\TeX\ uses the \verb+natbib+ package of Patrick Daly, 
its entire repertoire of commands are available in your document;
see the \verb+natbib+ documentation for further details.
The argument of \verb+\cite+ is a comma-separated list of \emph{keys};
a key may consist of letters and numerals.

By default, citations are numerical; \cite{feyn54} author-year citations are an option. 
To give a textual citation, use \verb+\onlinecite{#1}+: (Refs.~\onlinecite{witten2001,epr,Bire82}). 
REV\TeX\ ``collapses'' lists of consecutive numerical citations when appropriate. 
REV\TeX\ provides the ability to properly punctuate textual citations in author-year style;
this facility works correctly with numerical citations only with \texttt{natbib}'s compress option turned off. 
To illustrate, we cite several together \cite{feyn54,witten2001,epr,Berman1983}, 
and once again (Refs.~\onlinecite{epr,feyn54,Bire82,Berman1983}). 
Note that, when numerical citations are used, the references were sorted into the same order they appear in the bibliography.

A reference within the bibliography is specified with a \verb+\bibitem{#1}+ command,
where the argument is the citation key mentioned above. 
\verb+\bibitem{#1}+ commands may be crafted by hand or, preferably,
generated by using Bib\TeX. 
The AIP styles for REV\TeX~4 include Bib\TeX\ style files
\verb+aipnum.bst+ and \verb+aipauth.bst+, appropriate for
numbered and author-year bibliographies,
respectively. 
REV\TeX~4 will automatically choose the style appropriate for 
the document's selected class options: the default is numerical, and
you obtain the author-year style by specifying a class option of \verb+author-year+.

This sample file demonstrates a simple use of Bib\TeX\ 
via a \verb+\bibliography+ command referencing the \verb+aipsamp.bib+ file.
Running Bib\TeX\ (in this case \texttt{bibtex
aipsamp}) after the first pass of \LaTeX\ produces the file
\verb+aipsamp.bbl+ which contains the automatically formatted
\verb+\bibitem+ commands (including extra markup information via
\verb+\bibinfo+ commands). If not using Bib\TeX, the
\verb+thebibiliography+ environment should be used instead.

\paragraph{Fourth-level heading is run in.}%
Footnotes are produced using the \verb+\footnote{#1}+ command. 
Numerical style citations put footnotes into the 
bibliography\footnote{Automatically placing footnotes into the bibliography requires using BibTeX to compile the bibliography.}.
Author-year and numerical author-year citation styles (each for its own reason) cannot use this method. 
Note: due to the method used to place footnotes in the bibliography, \emph{you
must re-run BibTeX every time you change any of your document's
footnotes}.

>>>>

\begin{abstract}
  El problema de \textit{Selección de Instancias} (IS por sus siglas en inglés), busca
  escoger un subconjunto de instancias de menor cardinalidad del conjunto original
  que mantenga o mejore la clasificación de las muestras a ser usadas como un conjunto
  de entrenamiento. En este articulo se considera la resolución de este problema
  mediante varios algoritmos metaheurísticos, finalizando con los resultados 
  experimentales y comparaciones entre ellos.
\end{abstract}

@@

\section{\label{sec:level1} Definición del Problema}

Un conjunto de datos se define en función de un conjunto de clases $\Omega$ y
un conjunto de $n$ observaciones $T$. Un problema de SI se define entonces como dicho 
conjunto de instancias 
$T = \{t_{1}, t_{2},..., t_{n}\}$, donde una instancia (observación) $t_{i}$ es
una tupla $t_{i} = (v_{i,1}, v_{i,2},...,v_{i,m})$ de $m$ valores/mediciones
(un punto en un espacio m-dimensional). Además, cada instancia $t_{i}$
pertenece a una clase $w_{t_{i}}  \epsilon  \Omega$.

La idea es seleccionar un subconjuto de menor cardinalidad 
$R \subseteq T$ tal que $R$ mantega o mejore la capacidad 
de representación del conjunto $T$.

@@

\subsubsection{\label{sec:level3}Representación}

Sea un conjunto inicial $T$, una solución al problema de SI está
dado por un subconjuto de instancias $R$,
que puede ser fácilmente representado por una cadena de bits de 
tamaño $n = |T|$ donde cada bit tiene valor 1/0, indicando respectivamente,
la pertenencia o no de una instancia $t_{i} \epsilon T$ en la solución.
